### 2021-03-29 ch02_scientific_background/scientific_background.tex
Cleaned tex files (hyphens, acronyms, etc.)

The first numerical climate models came up in the 1960s and were based on
weather prediction models \autocite{Flato2011}. Early models from the 1970s
simulated only the physical components of the climate system: atmosphere, land
surface, ocean and sea ice (see \cref{fig:02:esms_historical_evolution}). These
models are called \emph{\acp{AOGCM}} \autocite{Flato2013}. Over the course of
the years, climate models became more and more complex by including a wider
range of processes within the components, but also by introducing new
components to the coupled system. Examples of these are aerosols, the carbon
cycle, a dynamic vegetation, atmospheric chemistry and land ice (see
\cref{fig:02:esms_historical_evolution}). \Acp{AOGCM} coupled to these
additional components are called \emph{\acfp{ESM}}, which are the current
state-of-the-art models that allow the most sophisticated simulations of the
Earth's climate. In contrast to \acp{AOGCM}, \acp{ESM} enable the simulation of
biological and chemical processes in addition to the dynamics of the physical
components of the Earth system. Especially in the context of anthropogenic
climate change, these additional processes are of uttermost importance for
realistic climate model simulations, since the anthropogenic interference with
the Earth system directly influences the various biogeochemical cycles of the
Earth. For example, the emission of the most prominent \ac{GHG}, \ac{CO2},
immediately impacts the global carbon cycle by inserting additional carbon into
the system (see \cref{sec:02:carbon_cycle} for details). Further examples
include land use changes like the deforestation of tropical rainforests, which
also directly influences several biogeochemical cycles (\eg{} carbon cycle,
nitrogen cycle, phosphorus cycle, \etc{}) by altering respective sinks and
sources.

@@

A further metric describing the climate sensitivity is the \emph{\ac{TCR}}. In
contrast to the \ac{ECS}, this metric does not assume radiative equilibrium of
the Earth system but describes the transient response of an evolving climate.
Following \textcite{Bindoff2013}, \ac{TCR} is defined as the change in the
\ac{GSAT} at the time of \ac{CO2} doubling in a simulation with a $1 \unit{\%}$
per year increase of the atmospheric \ac{CO2} concentration (\onepctcotwo{}).
For this, the annual mean \acp{GSAT} are averaged over a 20 year period
centered at the time of the \ac{CO2} doubling (years \range{61}{80} when the
first year is indexed with $1$). To account for model drift, the annual mean
changes in \ac{GSAT} are calculated relative to a corresponding pre-industrial
control simulation smoothed with a linear fit that considers 140 model years
(length of the \onepctcotwo{} simulation). An illustration of that calculation
is shown in \cref{fig:02:tcr}.

>>>>

The first numerical climate models came up in the 1960s and were based on
weather prediction models \autocite{Flato2011}. Early models from the 1970s
simulated only the physical components of the climate system: atmosphere, land
surface, ocean and sea ice (see \cref{fig:02:esms_historical_evolution}). These
models are called \emph{\acfp{AOGCM}} \autocite{Flato2013}. Over the course of
the years, climate models became more and more complex by including a wider
range of processes within the components, but also by introducing new
components to the coupled system. Examples of these are aerosols, the carbon
cycle, a dynamic vegetation, atmospheric chemistry and land ice (see
\cref{fig:02:esms_historical_evolution}). \Acp{AOGCM} coupled to these
additional components are called \emph{\acfp{ESM}}, which are the current
state-of-the-art models that allow the most sophisticated simulations of the
Earth's climate. In contrast to \acp{AOGCM}, \acp{ESM} enable the simulation of
biological and chemical processes in addition to the dynamics of the physical
components of the Earth system. Especially in the context of anthropogenic
climate change, these additional processes are of uttermost importance for
realistic climate model simulations, since the anthropogenic interference with
the Earth system directly influences the various biogeochemical cycles of the
Earth. For example, the emission of the most prominent \ac{GHG}, \ac{CO2},
immediately impacts the global carbon cycle by inserting additional carbon into
the system (see \cref{sec:02:carbon_cycle} for details). Further examples
include land use changes like the deforestation of tropical rainforests, which
also directly influences several biogeochemical cycles (\eg{} carbon cycle,
nitrogen cycle, phosphorus cycle, \etc{}) by altering respective sinks and
sources.

@@

A further metric describing the climate sensitivity is the \emph{\ac{TCR}}. In
contrast to the \ac{ECS}, this metric does not assume radiative equilibrium of
the Earth system but describes the transient response of an evolving climate.
Following \textcite{Bindoff2013}, \ac{TCR} is defined as the change in the
\ac{GSAT} at the time of \ac{CO2} doubling in a simulation with a $1 \unit{\%}$
per year increase of the atmospheric \ac{CO2} concentration (\onepctcotwo{}).
For this, the annual mean \acp{GSAT} are averaged over a 20-year period
centered at the time of the \ac{CO2} doubling (years \range{61}{80} when the
first year is indexed with $1$). To account for model drift, the annual mean
changes in \ac{GSAT} are calculated relative to a corresponding pre-industrial
control simulation smoothed with a linear fit that considers 140 model years
(length of the \onepctcotwo{} simulation). An illustration of that calculation
is shown in \cref{fig:02:tcr}.
